---
title: "DQ report"
author: "GEEKS group 2"
format: html
execute: 
  echo: false
  warning: false
---

## Quarto

```{r}
library(tidyverse)
library(reactable)
library(flextable)
library(scales)
library(bslib)
library(shiny)
library(bsicons)
```

```{r}
data <- read.csv("./data/dhis2-data2.csv")

library(dplyr)

data_clean  <- data |> rowwise() |> 
  mutate(District = str_remove_all(District, " District"),
         missing_reports = Expected.reports - Actual.reports, 
         missing_reports = if_else(missing_reports == 0, FALSE, TRUE),
         neg_dropout_rate_dpt1_3 = if_else(dropout.rate >= 0, FALSE, TRUE),
         discrepancy_dpt3_pcv3 = DPT3 - PCV.3, 
         discrepancy_dpt3_pcv3 = if_else(discrepancy_dpt3_pcv3 == 0, FALSE, TRUE),
         neg_wastage_rates_dpt = if_else(wastage.rate >= 0, FALSE, TRUE),
         .keep = "unused") |> 
  filter( !(is.na(missing_reports)& is.na(neg_dropout_rate_dpt1_3)& is.na(discrepancy_dpt3_pcv3) & is.na(neg_wastage_rates_dpt)))

## 
final_df <- data_clean  |>  
  mutate(priorty_number = sum(missing_reports, neg_dropout_rate_dpt1_3, 
                            discrepancy_dpt3_pcv3, neg_wastage_rates_dpt, na.rm = T)) |> 
  arrange(desc(priorty_number))

```

```{r}

percentage <- function(indicator){
  round((sum(indicator, na.rm = T)/n())*100, digits= 1)
}


district_data <- final_df |> 
  group_by(District) |> 
  summarise(across(missing_reports:neg_wastage_rates_dpt, percentage)) |> 
  arrange(across(missing_reports:neg_wastage_rates_dpt, desc))
  #arrange(desc(missing_reports), desc(neg_dropout_rate_dpt1_3), desc(discrepancy_dpt3_pcv3),desc(neg_wastage_rates_dpt))

```

```{r}
colourer <- col_quantile(
  palette = c("RdYlGn"),
  reverse = TRUE,
  domain = c(0, 100))
```

```{r}
std_border <- fp_border_default(width = 2, color = "white")

ft <- flextable( district_data)

 # ft |> 
 #  bg(bg = colourer,
 #     j = c("missing_reports","neg_dropout_rate_dpt1_3","discrepancy_dpt3_pcv3",  "neg_wastage_rates_dpt")) %>%
 #   bg(bg = colourer,
 #     j = c("missing_reports","neg_dropout_rate_dpt1_3","discrepancy_dpt3_pcv3",  "neg_wastage_rates_dpt")) |> 
 #  fontsize( size = 10, part = "all") |> 
 #  font(fontname = "Courier", part = "all") |> 
 #   align(align = "center", part = "all") |> 
 #  bold() |> 
 #  # color(color = "white", part = "body") |> 
 #  #  color(color = "black",part = "header") |> 
 #   border_outer(part = "all", border = std_border) %>%
 #   border_inner(border = std_border, part = "all") |> 
 #   height(height = .5) %>%
 #   width(width = .5) |> 
 #   hrule(rule = "exact", part = "body")
  

```

::: {.callout-note}
Note that there are five types of callouts, including:
`note`, `warning`, `important`, `tip`, and `caution`.
:::

::: {.callout-tip}
## Tip with Title

This is an example of a callout with a title.
:::

::: {.callout-caution collapse="true"}
## Expand To Learn About Collapse

This is an example of a 'folded' caution callout that can be expanded by the user. You can use `collapse="true"` to collapse it by default or `collapse="false"` to make a collapsible callout that is expanded by default.
:::


```{r}
theme_design <- function(x) {
  
  
  x <- border_remove(x)
  std_border <- fp_border_default(width = 4, color = "white")
  x <- fontsize(x, size = 10, part = "all")
  x <- font(x, fontname = "Courier", part = "all")
  x <- align(x, align = "center", part = "all")
  x <- bold(x, bold = TRUE, part = "all")
  x <- bg(x, bg = "#475f77", part = "body", j = c("District"))
  x <-  bg(x, bg = scales::col_quantile(palette = c("RdYlGn"), reverse = TRUE,domain = c(0, 100)),
           j = c("missing_reports","neg_dropout_rate_dpt1_3","discrepancy_dpt3_pcv3",  "neg_wastage_rates_dpt"))
  x <- bg(x, bg = "#1bbbda", part = "header")
  x <- bg(x, bg = "#1bbbda", part = "footer")
  x <- color(x, color = "white", part = "all")
  x <- padding(x, padding = 6, part = "all")
  x <- border_outer(x, part="all", border = std_border )
  x <- border_inner_h(x, border = std_border, part="all")
  x <- border_inner_v(x, border = std_border, part="all")
  x <- set_table_properties(x, layout = "fixed")
  x
}
```

```{r}
ft <- flextable( district_data)

 ft |> 
   theme_design()
```

```{r}
 district_data |> 
  mutate(missing_reports = if_else(missing_reports >= 50, TRUE, FALSE),
         neg_dropout_rate_dpt1_3 = if_else(neg_dropout_rate_dpt1_3 >= 50, TRUE, FALSE),
         discrepancy_dpt3_pcv3 = if_else(discrepancy_dpt3_pcv3 >= 50, TRUE, FALSE),
         neg_wastage_rates_dpt = if_else(neg_wastage_rates_dpt >= 50, TRUE, FALSE),
         .keep = "unused") |> 
  summarise(across(missing_reports:neg_wastage_rates_dpt, sum, na.rm = T))
  
```


